The Minimum Vertex Cover problem and its weighted variant are NP-Complete problems with several known linear time sequential algorithms that provide constant factor approximations. The existence of such algorithms suggests that it should be theoretically possible to discover a distributed or parallel algorithm to provide a constant factor approximation in constant time, however, it has been proven that no such algorithm exists\cite{1011811}. 

Here we present a distributed algorithm that provides a 2-optimal solution to Minimum Weighted Vertex Cover(MWVC) in $O(\log\Delta)$ rounds with high probability, where $\Delta$ is the largest degree of the graph. This algorithm, based on maximal matchings, is the first distributed algorithm that we are aware of with a performance based on $\Delta$ rather than on the size of the graph. We extend our framework for this algorithm and show how it can be applied to the Minimum Edge Coloring problem and the Strong Directed Edge Coloring problem. This work is an extension of our work in \cite{Daigle:2011uq, Daigle:2012uq}. We have added formal proofs for correctness and performance of the edge coloring algorithm and included new experimental results for our vertex covering algorithm. 

Our primary practical result is the distributed algorithm for MWVC. This algorithm improves on existing work by reducing the communication rounds from $O(\log n)$ to $O(\log \Delta)$. We verify our findings theoretically and through experiment. In addition, we present what we believe to be the first distributed algorithm for Strong Directed Edge Coloring which requires only distance 1 information and solves in $O(\Delta)$ rounds.
